---
title: "CV_DataPrep_20201108"
author: "CWBrink_list"
date: "08/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The effect of supplementary feeding on Cape Vulture breeding success

Supplementary feeding has become a popular, yet still debated, conservation tool to mitigate Old World vulture declines. This intervention is proposed to support vulture numbers by increasing various demographic parameters but such effects have seldom been verified. I used monitoring data on ten South African Cape Vulture colonies spanning over two decades, to model the relationship between supplementary feeding sites within a 100 or 200 km radius and breeding success. 

This code prepares the data for the above mentioned analysis and entails the creation of the following variables for both the 100 and 200 km buffer:

1) Ammount of food provided inside buffer
2) Proximity indices per year
3) Ammount of unsafe food provided (lead and veterianry drugs seperately)
4) Poisoning probability estimate 

```{r Libraries}

rm(list=ls())

pck <- c("lme4", "tidyverse", "MuMIn", "list", "GGally", "broom", 
         "caret", "parallel", "mgcv", "gstat", "fasterize", "viridis", "car", 
         "PerformanceAnalytics", "readr", "sf", "sp", "raster", "spData", 
         "ggspatial", "here", "xtable", "rgdal", "rgeos", "lwgeom", "ggmap", "raster")

lapply(pck, library, character.only= TRUE)

```


```{r Custom functions}

see <- function(x) utils::View(x)

```

```{r Data import}

options(scipen=999)

sfs.dat <- read_csv(here("Data", "SFSDatabase_2020_forChpt4.csv"))
sfs.dat <- as.data.frame(sfs.dat)

sfs.survey.add <- read.csv(here("Data", "LeadVetD_data_for_addition_toSFSdata_20201116.csv"))
sfs.survey.add <- as.data.frame(sfs.survey.add)

bs.dat <- read_csv(here("Data", "SummaryData_from_Tapiwa", "Test_data_AWBV.csv"))
bs.dat <- as.data.frame(bs.dat)

bs.cv <- read_csv(here("Data", "BSdata_checked", "BS_CV_newdata_cwb_20210117.csv"))
bs.cv <- as.data.frame(bs.cv)
bs.cv <- dplyr::select(bs.cv, -Notes)

# No coordinates in the summary data, need to do from the start
bc.dat <- read_csv(here("Data", "SAFRING_106&107_Chick data_accquired20201005.csv"))  
bc.dat <- as.data.frame(bc.dat)

```

# Data preperation

## Prep

```{r}
bc.dat <- bc.dat %>% separate(., col = "Location_codeB", into = c("Y", "X"), sep = "S", remove = FALSE)
bc.dat$X <- lapply(bc.dat$X, gsub, pattern = "E", replacement = "")

#converting to decimal degrees

coord_convert <- function(angle) {
  angle <- as.character(angle)
  x <- do.call(rbind, strsplit(angle, split=' '))
  x <- apply(x, 1L, function(y) {
    y <- as.numeric(y)
    y[1] + y[2]/60
  })
  return(x)
}

bc.dat$X <- coord_convert(bc.dat$X)
bc.dat$Y <- coord_convert(bc.dat$Y)
bc.dat$Y <- bc.dat$Y*(-1)

```


## Filtering

```{r Filtering SFS and adding data}

sfs.dat <- left_join(sfs.dat, sfs.survey.add, by = c("VulPro_Code"="VR_Code"))

sfs.dat <- sfs.dat %>%
  mutate(Aware_lead = ifelse(Lead == "Yes", 1, ifelse(Lead == "Don't know" | Lead == "No", 0, NA))) %>% 
  mutate(Aware_drugs = ifelse(Drugs == "Yes", 1, ifelse(Drugs == "Don't know" | Drugs == "No", 0, NA)))

sfs.dat <- sfs.dat %>% dplyr::select(., -c("Province.y", "Lead", "Drugs", "Directions to get there"))

sfs.dat <- sfs.dat %>% filter(., Structure == "SFS") %>% 
                        filter(., is.na(Closure_date) |Closure_date > 2000) %>% 
                        filter(., Latitude != "NA" & Longitude != "NA") %>% 
                        filter(., Status_Category != "Unknown" | Status_Category != "Not SFS") %>% 
                        filter(., !(Status_Category == "Closed" &  Closure_date < 2000)) 
                       # filter(., Country == "South Africa" | Country = )

```

```{r Filtering Body Condition}

bc.dat.wbv <- bc.dat %>% filter(., Spp == "107") %>% 
                      filter(., Age == 1 | Age == 5) %>% # Age 1 = Nestling, Age 5 = 0-6 months
                      filter(., Mass != "NA") %>% 
                      filter(., Wing != "NA") %>% 
                      filter(., Mass > 0) %>% 
                      filter(., Wing > 0) %>% 
                      filter(., Cond == 0) %>% 
                      filter(., Code == 1) %>% 
                      filter(., Country == "South Africa")

bc.dat.awb <- bc.dat %>% filter(., Spp == "106") %>% 
                      filter(., Age == 1 | Age == 5) %>% 
                      filter(., Mass != "NA") %>% 
                      filter(., Wing != "NA") %>% 
                      filter(., Mass > 0) %>% 
                      filter(., Wing > 0) %>% 
                      filter(., Code == 1)

```


## Spatial data and Reprojection

```{r Reprojections}

crs_options = rgdal::make_EPSG() # list of all projections available in R
#see(crs_options)

crs_utm <-  CRS("+init=epsg:32735") 
# EPSG:4326 - WGS 84 - Geographic Unit= degrees; EPSG: 32735 WGS 84 UTM35 Projected Unit=meters ~ proj4string of coords

SA <- readRDS(here("Data", "Spatial_data", "SA_baseMaps", "gadm36_ZAF_0_sf.rds"))
SA = st_transform(SA, 32735)
Prov <- readRDS(here("Data", "Spatial_data", "SA_baseMaps","gadm36_ZAF_1_sf.rds"))
Prov = st_transform(Prov, 32735) # transforming to projected CRS WGS84 UTM35S, the number is the EPSG code

Poison <- raster(here("Data", "Spatial_data", "FiveYear_PoisoningPrev_clippedRaster_chpt4.tif"))
Poison <- projectRaster(Poison, crs = crs(Prov))

crs(Poison)

# st_set_crs()
# st_crs(Prov)

SFS <-  st_as_sf(sfs.dat, coords = c("Longitude", "Latitude"), crs = 4326)
SFS = st_transform(SFS, 32735)

bs.dat.sp <- st_as_sf(bs.dat, coords = c("longitude", "latitude"), crs = 4326)
bs.dat.sp = st_transform(bs.dat.sp, 32735)

bs.cv.sp <- st_as_sf(bs.cv, coords = c("longitude", "latitude"), crs = 4326) 
bs.cv.sp = st_transform(bs.cv.sp, 32735)


bc.dat.wbv <- st_as_sf(bc.dat.wbv, coords = c("X", "Y"), crs = 4326)
bc.dat.wbv = st_transform(bc.dat.wbv, 32735)

```

# AWB Vultures
## Buffer

```{r Buffers}

bs.buff100 <- st_buffer(bs.dat.sp, dist = 100000)
bs.buff200 <- st_buffer(bs.dat.sp, dist = 200000)

```

```{R Maps, eval=FALSE} 

ggplot() +
  geom_sf(data = Prov) +
  geom_sf(data = bc.dat.wbv, color = "blue") +
  geom_sf(data = SFS, color = "green") +
  geom_sf(data = bs.buff100, fill = "red", alpha = 0.1) +
  geom_sf(data = bs.dat.sp, color = "black") +
  geom_sf(data = bs.cv.sp, color = "yellow") +
  ggtitle("Map of Plot Locations")

ggplot() +
  geom_sf(data = Prov) +
  geom_raster(data = Poison_df, aes(x = x, y = y, fill = FiveYear_PoisoningPrev_clippedRaster_chpt4)) + 
  geom_sf(data = bs.dat.sp) +
  geom_sf(data = bs.buff100, fill = "blue", alpha = 0.1) +
  geom_sf(data = SFS, color = "green") +
  ggtitle("Map of Plot Locations") 
  
# plotting raster
  # convert to a df for plotting in two steps, 1)to SpatialPointsDataFrame 2) to conventional dataframe
  
Poison_pts <- rasterToPoints(Poison, spatial = TRUE)
Poison_df <- data.frame(Poison_pts)
  
ggplot() +  
  geom_raster(data = Poison_df, aes(x = x, y = y, fill = FiveYear_PoisoningPrev_clippedRaster_chpt4))

```


# Creating breeding success data set

```{r Exploring components of For Loop, eval=FALSE}
#################################
#Doing the filtering outside a loop for single colony, single year.
#################################

#subset SFS for specific year
SFS_2012 <- filter(SFS, (Establishment_date < 2012 & Closure_date > 2012) | (Status_Category == "Active" & Establishment_date == "NA"))

# applying to bs data:

# Sequence:
#1) Selct colony and year
Buff100_2012MLK <- bs.buff100 %>% filter(., conca == "2012MKL")
#2) Extract all SFS in buffer of that colony
SFS_b = SFS[Buff100_2012MLK, ]
#3) Filter out only SFS active in same year in question
# - Active with no dates = assume it was active in period
# - Closed with no dates = assume it was closed in period
# justification: closed SFS with little data often were never even SFS to start with, ones verrified as active are definately SFS
SFS_bf <- SFS_b %>% filter(., 
(Establishment_date < Buff100_2012MLK$year | is.na(Establishment_date)) & (Closure_date > Buff100_2012MLK$year | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)), 
                        Status_Category != "Unknown", 
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))

Buff100_2012MLK <- Buff100_2012MLK %>% mutate(., Total_kg_y = sum(SFS_bf$Total_kg_y))

test <- SFS[bs.buff100[20, ], ] # this seems to filter SFS by the colony buffer in question
```


# Creating BREEDING SUCCESS data set

Bat paper formula: Esselstyn et al 2004 "Habitat use of the Pacific sheath-tailed bat (Emballonura semicaudata) on Aguiguan, Mariana Islands". Proximity = (sum((1/distance^2)*food provided))/numberofSFS

```{r 100 km Proximity Index etc}


# making lists for the for loops
# should we be using average in buffer, average of all, average of those active in that year?

ProvBuf <- list()

for(col in unique(bs.buff100$conca)){
######################################### Spatial filter  
  buffer = filter(bs.buff100, conca == col)
  
  colony_sfs <- filter(SFS,
    (Establishment_date < buffer$year | is.na(Establishment_date)) & (Closure_date > buffer$year | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
  avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 
  
  colony_sfs_rel = colony_sfs[buffer, ]
  
######################################## SFS number and Total Provisioning  
  SFS_noPR_number <- colony_sfs_rel %>% filter(., is.na(Total_kg_y)) %>% nrow(.)
  SFS_number <- nrow(colony_sfs_rel)
  
  colony_sfs_rel <- colony_sfs_rel %>% mutate_at(vars("Total_kg_y"), ~replace(., is.na(.), avg_pr)) # adding average ProvR to SFS without any
  
  Food <- sum(colony_sfs_rel$Total_kg_y) 
  
  Lead_food <- colony_sfs_rel %>% filter(., Aware_lead == 0)
  Lead_food <- sum(Lead_food$Game_kg_y)
  Lead_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_lead)) %>% nrow()
  
  Drugs_food <- colony_sfs_rel %>% filter(., Aware_drugs == 0) 
  Drugs_food <- sum(Drugs_food$Total_kg_y - Drugs_food$Game_kg_y)
  Drugs_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_drugs)) %>% nrow()
  
##################################### Poisoning Probability
  
AvgPoison <- as.vector(extract(Poison, buffer, fun = mean, na.rm = TRUE))

b_code <- col
  
########################################## Proximity Index  
ProxIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.dat.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v1 <- (1/(st_distance(VR, colony.point))^2)*VR$Total_kg_y
    
    ProxIndex[[sfs]] <- v1
  }
  PI_step1 <- as.data.frame(do.call(rbind, ProxIndex))
  PI <- sum(PI_step1)/nrow(colony_sfs_rel)
  
###########################################
  ProvBuf[[col]] <- c(b_code, SFS_number, SFS_noPR_number, PI, Food, Lead_food, Drugs_food, Lead_answered, Drugs_answered, AvgPoison)
}

Results.bs.100 <- as.data.frame(do.call(rbind,  ProvBuf))
Results.bs.100 <- rename(Results.bs.100, b_code = V1, SamllB_SFS_number = V2, SamllB_SFS_noPR_number = V3, SamllB_PI  = V4, SamllB_Total_kg_y = V5, SamllB_Lead_foodkgy = V6, SamllB_Drugs_foodkgy = V7, SamllB_Lead_answered = V8, SamllB_Drugs_answered = V9, SamllB_AvgPoison = V10)

bs.dat2 <- left_join(bs.dat, Results.bs.100, by = c("conca"="b_code"))

```

```{r 200 km Proximity Index etc}

ProvBuf <- list()

for(col in unique(bs.buff200$conca)){
######################################### Spatial filter  
  buffer = filter(bs.buff200, conca == col)
  
  colony_sfs <- filter(SFS,
    (Establishment_date < buffer$year | is.na(Establishment_date)) & (Closure_date > buffer$year | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
  avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 
  
  colony_sfs_rel = colony_sfs[buffer, ]
  
######################################## SFS number and Total Provisioning  
  SFS_noPR_number <- colony_sfs_rel %>% filter(., is.na(Total_kg_y)) %>% nrow(.)
  SFS_number <- nrow(colony_sfs_rel)
  
  colony_sfs_rel <- colony_sfs_rel %>% mutate_at(vars("Total_kg_y"), ~replace(., is.na(.), avg_pr)) # adding average ProvR to SFS without any
  
  Food <- sum(colony_sfs_rel$Total_kg_y) 
  
  Lead_food <- colony_sfs_rel %>% filter(., Aware_lead == 0)
  Lead_food <- sum(Lead_food$Game_kg_y)
  Lead_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_lead)) %>% nrow()
  
  Drugs_food <- colony_sfs_rel %>% filter(., Aware_drugs == 0) 
  Drugs_food <- sum(Drugs_food$Total_kg_y - Drugs_food$Game_kg_y)
  Drugs_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_drugs)) %>% nrow()
  
##################################### Poisoning Probability
  
  AvgPoison <- as.vector(extract(Poison, buffer, fun = mean, na.rm = TRUE))

  b_code <- col
  
########################################## Proximity Index  
ProxIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.dat.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v1 <- (1/(st_distance(VR, colony.point))^2)*VR$Total_kg_y
    
    ProxIndex[[sfs]] <- v1
  }
  PI_step1 <- as.data.frame(do.call(rbind, ProxIndex))
  PI <- sum(PI_step1)/nrow(colony_sfs_rel)
  
###########################################
  ProvBuf[[col]] <- c(b_code, SFS_number, SFS_noPR_number, PI, Food, Lead_food, Drugs_food, Lead_answered, Drugs_answered, AvgPoison)
}

Results.bs.200 <- as.data.frame(do.call(rbind,  ProvBuf))
Results.bs.200 <- rename(Results.bs.200, b_code = V1, BigB_SFS_number = V2, BigB_SFS_noPR_number = V3, BigB_PI  = V4, BigB_Total_kg_y = V5, BigB_Lead_foodkgy = V6, BigB_Drugs_foodkgy = V7, BigB_Lead_answered = V8, BigB_Drugs_answered = V9, BigB_AvgPoison = V10)

bs.dat2 <- left_join(bs.dat2, Results.bs.200, by = c("conca"="b_code"))

write.csv(bs.dat2, here("Outputs", "Data_output", "BreedingSuccess_PI.csv"))

```

```{r Double checking Results for individual buffers, eval=FALSE}


sfs.test <- filter(SFS,
    (Establishment_date < 2015 | is.na(Establishment_date)) & (Closure_date > 2015 | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))

buf.test <-  bs.buff100 %>% filter(., conca == "2015BNM")

t = sfs.test[buf.test, ]

ggplot() +
  geom_sf(data = Prov) +
  geom_sf(data = sfs.test, color = "black") +
 # geom_sf(data = bs.dat.sp) +
  geom_sf(data = buf.test, fill = "blue", alpha = 0.05) +
  ggtitle("Map of Plot Locations")

```

## Test Prox Index

Below I test Proximity Index calculations and see if my loop results match those done by hand. The loop seems to be working correctly.

```{r Testing PI by hand, eval=FALSE}

# 2017VLK
buf.test <- filter(bs.buff100, conca == "2017VLK")
col.point.test <-  filter(bs.dat.sp, conca == "2017VLK")

colony_sfs <- filter(SFS,
    (Establishment_date < 2017 | is.na(Establishment_date)) & (Closure_date > 2017 | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 


colony_sfs_test = colony_sfs[buf.test, ]

st_distance(colony_sfs_test, col.point.test)



q <- ((1/(51495.30)^2)*33750) + ((1/(69916.31)^2)*7076.441) + ((1/(21758.42)^2)*18676.408) + ((1/(71953.47)^2)*3600) + ((1/(49146.49)^2)*1000)

q/5 # 0.00001094672 Same as loop
    # 0.0000109467209782848

# 2011MKL

buf.test <- filter(bs.buff100, conca == "2011MKL")
col.point.test <-  filter(bs.dat.sp, conca == "2011MKL")

colony_sfs <- filter(SFS,
    (Establishment_date < 2011 | is.na(Establishment_date)) & (Closure_date > 2011 | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 


colony_sfs_test = colony_sfs[buf.test, ]

st_distance(colony_sfs_test, col.point.test)



q <- ((1/(58862.95)^2)*6491.525) + ((1/(55281.05)^2)*1080) 
  
q/2 # 0.000001113471
    # 0.00000111347118096256 (same as my loop)


# 2015BNM

buf.test <- filter(bs.buff100, conca == "2015BNM")
col.point.test <-  filter(bs.dat.sp, conca == "2015BNM")

colony_sfs <- filter(SFS,
    (Establishment_date < 2015 | is.na(Establishment_date)) & (Closure_date > 2015 | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 


colony_sfs_test = colony_sfs[buf.test, ]

st_distance(colony_sfs_test, col.point.test) #~ not working



q <- ((1/(21516.005)^2)*4666.681) + ((1/(46958.962)^2)*28731.146) + ((1/(93181.367)^2)*18991.99) + ((1/(18465.364)^2)*3000.000) + ((1/(6444.059)^2)*18991.99) + ((1/(8120.428)^2)*8800.000)
  
q/6 # 0.0001041501     (Same as loop)
    # 0.000104150060299384

```


# Cape Vultures

## Buffer

```{r Buffers}

bs.cv.b100 <- st_buffer(bs.cv.sp, dist = 100000)
bs.cv.b200 <- st_buffer(bs.cv.sp, dist = 200000)

```

```{R Maps} 

ggplot() +
  geom_sf(data = Prov) +
  geom_sf(data = bs.cv.sp, color = "blue") +
  geom_sf(data = filter(SFS, Country == "South Africa"), color = "green") +
  geom_sf(data = bs.cv.b200, fill = "blue", alpha = 0.01) +
  geom_sf(data = bs.cv.b100, fill = "red", alpha = 0.01) +
  #geom_sf(data = bs.dat.sp, color = "black") +
  ggtitle("Map of Plot Locations")

```

# Creating CV BREEDING SUCCESS data set

bat paper formula: Esselstyn et al 2004 "Habitat use of the Pacific sheath-tailed bat (Emballonura semicaudata) on Aguiguan, Mariana Islands". Proximity = (sum((1/distance^2)*food provided))/numberofSFS

```{r CV 100 km Proximity Index etc}

ProvBuf <- list()

for(col in unique(bs.cv.b100$conca)){
######################################### Spatial filter  
  buffer = filter(bs.cv.b100, conca == col)
  
  colony_sfs <- filter(SFS,
    (Establishment_date < buffer$year | is.na(Establishment_date)) & (Closure_date > buffer$year | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
  avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 
  
  colony_sfs_rel = colony_sfs[buffer, ]
  
######################################## SFS number and Total Provisioning  
  SFS_noPR_number <- colony_sfs_rel %>% filter(., is.na(Total_kg_y)) %>% nrow(.)
  SFS_number <- nrow(colony_sfs_rel)
  
  colony_sfs_rel <- colony_sfs_rel %>% mutate_at(vars("Total_kg_y"), ~replace(., is.na(.), avg_pr)) # adding average ProvR to SFS without any
  
  Food <- sum(colony_sfs_rel$Total_kg_y) 
  
  Lead_food <- colony_sfs_rel %>% filter(., Aware_lead == 0)
  Lead_food <- sum(Lead_food$Game_kg_y)
  Lead_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_lead)) %>% nrow()
  
  Drugs_food <- colony_sfs_rel %>% filter(., Aware_drugs == 0) 
  Drugs_food <- sum(Drugs_food$Total_kg_y - Drugs_food$Game_kg_y)
  Drugs_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_drugs)) %>% nrow()
  
  ##################################### Poisoning Probability
  
  AvgPoison <- as.vector(extract(Poison, buffer, fun = mean, na.rm = TRUE))

  b_code <- col
  
########################################## Proximity Index  
ProxIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.cv.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v1 <- (1/(st_distance(VR, colony.point))^2)*VR$Total_kg_y
    
    ProxIndex[[sfs]] <- v1
  }
  PI_step1 <- as.data.frame(do.call(rbind, ProxIndex))
  PI <- sum(PI_step1)/nrow(colony_sfs_rel)
    
########################################## Distance Index  
DistIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.cv.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v2 <- (1/(st_distance(VR, colony.point))^2)
    
    DistIndex[[sfs]] <- v2
  }
  DistI_step1 <- as.data.frame(do.call(rbind, DistIndex))
  DistI <- sum(DistI_step1)/nrow(colony_sfs_rel)
  
###########################################
  ProvBuf[[col]] <- c(b_code, SFS_number, SFS_noPR_number, PI, Food, Lead_food, Drugs_food, Lead_answered, Drugs_answered, AvgPoison, DistI)
}

Results.cv.bs100 <- as.data.frame(do.call(rbind,  ProvBuf))
Results.cv.bs100 <- rename(Results.cv.bs100, b_code = V1, SamllB_SFS_number = V2, SamllB_SFS_noPR_number = V3, SamllB_PI  = V4, SamllB_Total_kg_y = V5, SamllB_Lead_foodkgy = V6, SamllB_Drugs_foodkgy = V7, SamllB_Lead_answered = V8, SamllB_Drugs_answered = V9, SamllB_AvgPoison = V10, SamllB_DistI = V11)

bs.cv2 <- left_join(bs.cv, Results.cv.bs100, by = c("conca"="b_code"))

```

```{r CV 200 km Proximity Index etc}

ProvBuf <- list()

for(col in unique(bs.cv.b200$conca)){
######################################### Spatial filter  
  buffer = filter(bs.cv.b200, conca == col)
  
  colony_sfs <- filter(SFS,
    (Establishment_date < buffer$year | is.na(Establishment_date)) & (Closure_date > buffer$year | is.na(Closure_date))|
                          (Status_Category == "Active" & is.na(Establishment_date) & is.na(Closure_date)),
                        Status_Category != "Unknown",
                        !(Status_Category == "Closed" & is.na(Establishment_date) & is.na(Closure_date)))
  
  avg_pr <- mean(colony_sfs$Total_kg_y, na.rm = T) 
  
  colony_sfs_rel = colony_sfs[buffer, ]
  
######################################## SFS number and Total Provisioning  
  SFS_noPR_number <- colony_sfs_rel %>% filter(., is.na(Total_kg_y)) %>% nrow(.)
  SFS_number <- nrow(colony_sfs_rel)
  
  colony_sfs_rel <- colony_sfs_rel %>% mutate_at(vars("Total_kg_y"), ~replace(., is.na(.), avg_pr)) # adding average ProvR to SFS without any
  
  Food <- sum(colony_sfs_rel$Total_kg_y) 
  
  Lead_food <- colony_sfs_rel %>% filter(., Aware_lead == 0)
  Lead_food <- sum(Lead_food$Game_kg_y)
  Lead_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_lead)) %>% nrow()
  
  Drugs_food <- colony_sfs_rel %>% filter(., Aware_drugs == 0) 
  Drugs_food <- sum(Drugs_food$Total_kg_y - Drugs_food$Game_kg_y)
  Drugs_answered <- colony_sfs_rel %>% filter(., !is.na(Aware_drugs)) %>% nrow()
  
  ##################################### Poisoning Probability
  
  AvgPoison <- as.vector(extract(Poison, buffer, fun = mean, na.rm = TRUE))

  b_code <- col
  
########################################## Proximity Index  
ProxIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.cv.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v1 <- (1/(st_distance(VR, colony.point))^2)*VR$Total_kg_y
    
    ProxIndex[[sfs]] <- v1
  }
  PI_step1 <- as.data.frame(do.call(rbind, ProxIndex))
  PI <- sum(PI_step1)/nrow(colony_sfs_rel)
  
########################################## Dist Index  
DistIndex <- list() 
  
for(sfs in unique(colony_sfs_rel$SFS_Code)){
  
    VR <- filter(colony_sfs_rel, SFS_Code == sfs)
    
    colony.point <- filter(bs.cv.sp, conca == b_code)  # b_code doesnt change - keeps same b_code throughout loop
    
    v2 <- (1/(st_distance(VR, colony.point))^2)
    
    DistIndex[[sfs]] <- v2
  }
  DistI_step1 <- as.data.frame(do.call(rbind, DistIndex))
  DistI <- sum(DistI_step1)/nrow(colony_sfs_rel)
  
###########################################
  
  ProvBuf[[col]] <- c(b_code, SFS_number, SFS_noPR_number, PI, Food, Lead_food, Drugs_food, Lead_answered, Drugs_answered, AvgPoison, DistI)
}

Results.cv.bs200 <- as.data.frame(do.call(rbind,  ProvBuf))
Results.cv.bs200 <- rename(Results.cv.bs200, b_code = V1, BigB_SFS_number = V2, BigB_SFS_noPR_number = V3, BigB_PI  = V4, BigB_Total_kg_y = V5, BigB_Lead_foodkgy = V6, BigB_Drugs_foodkgy = V7, BigB_Lead_answered = V8, BigB_Drugs_answered = V9, BigB_AvgPoison = V10, BigB_DistI = V11)

bs.cv2 <- left_join(bs.cv2, Results.cv.bs200, by = c("conca"="b_code"))

write.csv(bs.cv2, here("Outputs", "Data_output", "BreedingSuccess_CV_PI_20210131.csv"))

```

```{r}

bs.dat2 <- bs.dat2 %>% 
  mutate_at(vars(starts_with("SamllB_")), funs(as.numeric)) %>% 
  mutate_at(vars(starts_with("BigB_")), funs(as.numeric)) %>% 
  mutate_at(vars("proxi100", "vr100"), funs(as.numeric))

bs.cv2 <- bs.cv2 %>% 
  mutate_at(vars(starts_with("SamllB_")), funs(as.numeric)) %>% 
  mutate_at(vars(starts_with("BigB_")), funs(as.numeric))

Results <- bind_rows(bs.dat2, bs.cv2)

Results <- Results %>% dplyr::select(-c("FID", "Active", "ob"))

write.csv(Results, here("Outputs", "Data_output", "BreedingSuccess_all_results.csv"))

```


